|

### 2022-12-30 paper.Rmd
Fri Dec 30 19:00:06 CET 2022: update-remote.sh

---
title: |
  <center>Pre-Trained Denoising Autoencoders Long Short-Term Memory Networks as probabilistic Models for Estimation of Distribution Genetic Programming</center>
  <center>Master Thesis - M.Sc. Business Education</center>
  <center>--------------------------------------------------------</center>
  <center>Student: Roman Höhn</center>
  <center>Date of Birth: 1991-04-14</center>
  <center>Place of Birth: Wiesbaden, Hesse</center>
  <center>Student ID: 2712497</center>
  <center>Supervisor: David Wittenberg</center>
  <center>--------------------------------------------------------</center>
  <center>Master Thesis</center>
  <center>FB 03: Chair of Business Administration and Computer Science</center>
  <center>Johannes Gutenberg University Mainz</center>
  |
date: "Date of Submission: `r Sys.Date()`"
output:
  pdf_document:
    # keep_tex: true
    extra_dependencies: ["float"]
    fig_caption: yes
    number_sections: true
    includes:
      in_header: [header_files/settings.tex]
indent: false
fontsize: 11pt
bibliography: ref/ref.bib
csl: csl/association-for-computing-machinery.csl
#csl: csl/harvard-cite-them-right.csl
#csl: csl/springer-science-reviews.csl
include-before: '`\thispagestyle{empty} \newpage{}`{=latex}'
---

@@

<!--- Explain algorithm and pre-training strategy in pseudo code -->

@@

![Flowchart - Regular DAE-GP](./img/flowcharts/dae-gp.png){height=800px width=200px}

>>>>

---
title: |
  <center>Pre-Trained Denoising Autoencoders Long Short-Term Memory Networks as probabilistic Models for Estimation of Distribution Genetic Programming</center>
  <center>Master Thesis - M.Sc. Business Education</center>
  <center>--------------------------------------------------------</center>
  <center>Student: Roman Höhn</center>
  <center>Date of Birth: 1991-04-14</center>
  <center>Place of Birth: Wiesbaden, Hesse</center>
  <center>Student ID: 2712497</center>
  <center>Supervisor: David Wittenberg</center>
  <center>--------------------------------------------------------</center>
  <center>Master Thesis</center>
  <center>FB 03: Chair of Business Administration and Computer Science</center>
  <center>Johannes Gutenberg University Mainz</center>
  |
date: "Date of Submission: `r Sys.Date()`"
output:
  pdf_document:
    # keep_tex: true
    extra_dependencies: ["float"]
    fig_caption: yes
    number_sections: true
    includes:
      in_header: [header_files/settings.tex]
indent: false
fontsize: 11pt
bibliography: ref/ref.bib
fig.width: 4in
fig.height: 3in
csl: csl/association-for-computing-machinery.csl
#csl: csl/harvard-cite-them-right.csl
#csl: csl/springer-science-reviews.csl
include-before: '`\thispagestyle{empty} \newpage{}`{=latex}'
---

@@

<!--- Explain algorithm and implementation of the pre-training strategy  -->

@@

![Flowchart - Regular DAE-GP](./img/flowcharts/dae-gp.png){height=900px width=200px}
